Interim Report WV

### 2015-03-29 tussentijdsverslag/tussentijdsverslag.tex
tussentijdsverslag

\section{Update}
Due neverending problems with over-the-air-deployment we decided to stop researching using Looci. We are now using just Contiki on the motes. We deploy components with the flasher.
\section{Interim Results}
In general all the results that we get from the OC and process with the Matlab script are negative. To interpret the results we just filipped the sign.
\subsection{RAM}
We wrote a component that writes 100 times 8kB to the RAM-memory, it repeats this action infinite times. Between the repetition the mote does nothing and is idle. We used the OC to measure a certain interval en we got the following results:\\
\\
-71.4368 -232.0165  -71.4722 -231.9092  -71.4422 -231.8196  -71.5196 -231.8710  -71.5787 -231.8401  -71.5961 -232.0866  -71.4173 -232.1306  -71.5185 -231.8660  -71.4893 -231.7818  -71.4970
\\
Energy when idle: $\pm 71 mj$\\
Energy when writing: $\pm 231 mj$
\subsection{Antenna}
\subsubsection{Enegry/byte}
We used the data provided at \url{http://people.cs.kuleuven.be/~wilfried.daniels/energy/results3.html} and used it to derive the energy cost per byte:
\includegraphics[width=\linewidth]{graph.png}
The average cost was: $0.00306399592 J/Byte.$
\subsubsection{Other aspects}
Next we also wanted to know the usage when the mote is listening and when it is idle. We wrote  a component that did nothing (with the antenna explicit off) and just used the pinflips, and anther with the antenna explicit on.
\subsubsection{Enegry when idle}
We got about the same energy usage as during the ram test when we wrote nothing:\\
-74.7316  -74.7610  -74.7003  -74.6391  -74.4582  -74.6195  -74.6579  -74.4509  -74.6454  -74.7656  -74.5681  -74.8548  -74.6121  -74.7943  -74.8279  -74.8777  -74.6717  -74.9203\\
\\
However as you can notice there is a tiny difference and we are not certain what the cause is?
\subsubsection{Enegry when listening}
During the listening test we got the following results:\\
-114.8897 -114.8994 -114.8356 -115.1350 -115.1103 -114.9205 -115.2339 -115.2512 -115.1336 -115.2102 -115.0942 -115.0485 -115.2242 -115.2833 -115.1356 -115.3479 -115.2736 -115.0013\\
\subsection{Energy to start the antenna}
%TODO 
\subsection{Flash}
As discussed with Klaas, we will only research this option when we have time.

\subsection{Interim Conclusion}
%TODO

\section{Questions}
\begin{itemize}
\item The results from our measurements, are they correct?
\item 
\end{itemize}
\end{document}

>>>>

\section{Update}
Due neverending problems with over-the-air-deployment we decided to stop researching using Looci. We are now using just Contiki on the motes. We deploy components with the flasher.
\section{Interim Results}
In general all the results that we get from the OC and process with the Matlab script are negative. To interpret the results we just filipped the sign.
\subsection{RAM}
We wrote a component that writes 100 times 8kB to the RAM-memory, it repeats this action infinite times. Between the repetition the mote does nothing and is idle. We used the OC to measure a certain interval en we got the following results:\\
\\
-71.4368 -232.0165  -71.4722 -231.9092  -71.4422 -231.8196  -71.5196 -231.8710  -71.5787 -231.8401  -71.5961 -232.0866  -71.4173 -232.1306  -71.5185 -231.8660  -71.4893 -231.7818  -71.4970
\\
\\
Energy when idle: $\pm 71 mj$\\
Energy when writing: $\pm 231 mj$
Energy for writing 1 byte: $ \frac{231-71 mj}{8*1000*100} \approx 0 mj$
\\
\\
We see that in fact writing a byte to RAM consumes almost no energy.
\subsection{Antenna}
\subsubsection{Enegry/byte}
We used the data provided at \url{http://people.cs.kuleuven.be/~wilfried.daniels/energy/results3.html} and used it to derive the energy cost per byte:
\includegraphics[width=\linewidth]{graph.png}
The average cost was: $0.00306399592 J/Byte.$
\subsubsection{Other aspects}
Next we also wanted to know the usage when the mote is listening and when it is idle. We wrote  a component that did nothing (with the antenna explicit off) and just used the pinflips, and anther with the antenna explicit on.
\subsubsection{Enegry when idle}
We got about the same energy usage as during the ram test when we wrote nothing:\\
-74.7316  -74.7610  -74.7003  -74.6391  -74.4582  -74.6195  -74.6579  -74.4509  -74.6454  -74.7656  -74.5681  -74.8548  -74.6121  -74.7943  -74.8279  -74.8777  -74.6717  -74.9203\\
\\
However as you can notice there is a tiny difference and we are not certain what the cause is?
\\ Another question that arises is that we in the component to write to RAM we didn't explicit turn the radio off, while the energy usage stayed the same?
\subsubsection{Enegry when listening}
During the listening test we got the following results:\\
-114.8897 -114.8994 -114.8356 -115.1350 -115.1103 -114.9205 -115.2339 -115.2512 -115.1336 -115.2102 -115.0942 -115.0485 -115.2242 -115.2833 -115.1356 -115.3479 -115.2736 -115.0013\\

\subsection{Flash}
As discussed with Klaas, we will only research this option when we have time. But it probably won't have any advantages:
\\
It most certainly will cost more to write to flash and if you can use half of the flash memory you only have 8 times more space to store data than if you write to RAM (assuming you also use only half the RAM).

\section{Interim Conclusion}

\section{Questions}
\begin{itemize}
\item The results from our measurements, are they correct?
\item How to measure the CPU usage as described before?
\end{itemize}
\end{document}
